\begin{frame}

\frametitle{Reading Material}

\footnotesize

\begin{itemize}

\item Charles W. Krueger. \emph{Software reuse}. ACM Comput. Surv. 24(2),
pp. 131--183. ACM, 1992.

\item John Hughes. \emph{Why functional programming matters}. The computer
journal 32(2), pp. 98--107. Oxford University Press, 1989.

\end{itemize}

Light reading:

\begin{itemize}

\item \texttt{oleks} \& \texttt{br0ns}. \emph{Unix-Like Data Processing
Utilities}. 2015. \url{http://atu15.onlineta.org/unix-like-data-processing.pdf}

\end{itemize}

\end{frame}


\begin{frame}

\frametitle{Video Material}

\footnotesize

\begin{itemize}

\item \emph{UNIX: Making Computers Easier To Use} --- AT\&T Archives film from
1982, Bell Laboratories. \url{https://youtu.be/XvDZLjaCJuw}.

\item Erlang Factroy SF 2016 --- Keynote --- John Hughes --- \emph{Why
Functional Programming Matters}. \url{https://youtu.be/Z35Tt87pIpg}.

\end{itemize}

\end{frame}


\begin{frame}

\frametitle{Summer Reading}

\footnotesize

C/C++:

\begin{itemize}

\item Andrew Koenig and Barbara E. Moo. \emph{Accelerated C++: Practical
Programming by Example}. Addison-Wesley, 2000.

\item Jens Gustedt. \emph{Modern C}. Unpublished, 2015. Latest version:
\url{http://icube-icps.unistra.fr/index.php/File:ModernC.pdf}.

\end{itemize}

C++ Templates:

\begin{itemize}

\item David Vandevoorde and Nicolai M. Josuttis. \emph{C++ Templates}.
Addison-Wesley, 2002.

\item Alexander Stepanov and Paul McJones. \emph{Elements of Programming},
Addison-Wesley, 2009.

\end{itemize}

\end{frame}
